### 2022-07-31 paper/akweury/document.tex
update an

	\centering
	\begin{tabular}{l l l l l l }
		\tabhead{Object} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{GCNN-NOC} & \tabhead{GCNN-CNN} & \tabhead{Trip-Net}\\
		Baoshanlu  & 38.53  &11.09 & 13.59 & 15.55 & 9.82\\ 
		\hline
		Bus & 32.61  & 7.82 & 8.98 & 11.95 & 7.35\\ 
		\hline
		Dragon &45.04& 10.61 & 15.31 & 16.05 & 7.35\\
		\hline
		Garfield & 42.15& 10.22 & 12.52 & 14.47 & 9.15\\
		\hline
		Washington &47.36 & 13.47 & 17.65 & 18.78 & 12.18\\
	\end{tabular}
	\caption{The performance of the GCNN model for geometry information based normal inference. The angle error is the average angle error of all valid pixels in the test case. bz stands for batch size, lr-schedule stands for learning rate schedule, lr-df stands for learning rate decay factor.}	
	\label{tab:gcnn-eval}
\end{table}

>>>>

	\centering
	\begin{tabular}{l l l l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{GCNN-NOC} & \tabhead{GCNN-CNN} & \tabhead{Trip-Net}\\
		Baoshanlu  		& 20 & 38.53  &11.09 & 13.59 & 15.55 & 9.82\\ 
		\hline
		Bus 			& 20 & 32.61  & 7.82 & 8.98 & 11.95 & 7.35\\ 
		\hline
		Dragon  		& 20 & 45.04& 10.61 & 15.31 & 16.05 & 7.35\\
		\hline
		Garfield 		& 20 & 42.15& 10.22 & 12.52 & 14.47 & 9.15\\
		\hline
		Washington 		& 20 & 47.36 & 13.47 & 17.65 & 18.78 & 12.18\\
	\end{tabular}
	\caption{Average Angle Error of the evaluation dataset.}	
	\label{tab:gcnn-eval-mean}
\end{table}

	\centering
	\begin{tabular}{l l l l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{GCNN-NOC} & \tabhead{GCNN-CNN} & \tabhead{Trip-Net}\\
		Baoshanlu  		& 20 & 38.53  &8.86 & 13.59 & 15.55 & 9.82\\ 
		\hline
		Bus 			& 20 & 32.61  & 4.44 & 4.44 & 11.95 & 7.35\\ 
		\hline
		Dragon	 		& 20 & 45.04 & 7.62 & 7.62 & 16.05 & 7.35\\
		\hline
		Garfield 		& 20 & 42.15 & 6.40 & 6.40 & 14.47 & 9.15\\
		\hline
		Washington 		& 20 & 47.36 & 7.64 & 17.65 & 18.78 & 12.18\\
	\end{tabular}
	\caption{Median Angle Error of the evaluation dataset.}	
	\label{tab:gcnn-eval-median}
\end{table}

	\centering
	\begin{tabular}{l l l l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{GCNN-NOC} & \tabhead{GCNN-CNN} & \tabhead{Trip-Net}\\
		Baoshanlu  		& 20 & 0.56  & 0.25 & 13.59 & 15.55 & 9.82\\ 
		\hline
		Bus 			& 20 & 32.61  & 0.56 & 8.98 & 11.95 & 7.35\\ 
		\hline
		Dragon 			& 20 & 45.04& 0.31 & 15.31 & 16.05 & 7.35\\
		\hline
		Garfield 		& 20 & 42.15& 0.41 & 12.52 & 14.47 & 9.15\\
		\hline
		Washington 		& 20 & 47.36 & 0.38 & 17.65 & 18.78 & 12.18\\
	\end{tabular}
	\caption{5 Average Angle Error of the evaluation dataset.}	
	\label{tab:gcnn-eval-d5}
\end{table}

	\centering
	\begin{tabular}{l l l l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{GCNN-NOC} & \tabhead{GCNN-CNN} & \tabhead{Trip-Net}\\
		Baoshanlu  	& 20 & 0.81 & 0.62 & 13.59 & 15.55 & 9.82\\ 
		\hline
		Bus 		& 20 & 32.61 & 0.81 & 8.98 & 11.95 & 7.35\\ 
		\hline
		Dragon 		& 20 & 45.04 & 0.69 & 15.31 & 16.05 & 7.35\\
		\hline
		Garfield 	& 20 & 42.15 & 0.72 & 12.52 & 14.47 & 9.15\\
		\hline
		Washington 	& 20 & 47.36 & 0.62 & 17.65 & 18.78 & 12.18\\
	\end{tabular}
	\caption{11.5 Average Angle Error of the evaluation dataset.}	
	\label{tab:gcnn-eval-d11}
\end{table}

	\centering
	\begin{tabular}{l l l l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{GCNN-NOC} & \tabhead{GCNN-CNN} & \tabhead{Trip-Net}\\
		Baoshanlu  & 20 & 0.90  &	0.90 & 13.59 & 15.55 & 9.82\\ 
		\hline
		Bus & 20 & 32.61  &			0.93 & 8.98 & 11.95 & 7.35\\ 
		\hline
		Dragon & 20 & 45.04& 		0.90 & 15.31 & 16.05 & 7.35\\
		\hline
		Garfield & 20 & 42.15& 		0.90 & 12.52 & 14.47 & 9.15\\
		\hline
		Washington & 20 & 47.36 &	0.81 & 17.65 & 18.78 & 12.18\\
	\end{tabular}
	\caption{22.5 Average Angle Error of the evaluation dataset.}	
	\label{tab:gcnn-eval-d22}
\end{table}

	\centering
	\begin{tabular}{l l l l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{GCNN-NOC} & \tabhead{GCNN-CNN} & \tabhead{Trip-Net}\\
		Baoshanlu  & 20 & 0.96  &0.96 & 13.59 & 15.55 & 9.82\\ 
		\hline
		Bus & 20 & 32.61  & 0.96 & 8.98 & 11.95 & 7.35\\ 
		\hline
		Dragon & 20 & 45.04& 0.95 & 15.31 & 16.05 & 7.35\\
		\hline
		Garfield & 20 & 42.15& 0.94 & 12.52 & 14.47 & 9.15\\
		\hline
		Washington & 20 & 47.36 &0.88 & 17.65 & 18.78 & 12.18\\
	\end{tabular}
	\caption{30 Angle Error of the evaluation dataset.}	
	\label{tab:gcnn-eval-d30}
\end{table}
